### 2021-10-20 docs/manuscript/manuscript.tex
Explain multi-input morphogen concentration
Improve mutation description

In our model the morphogen could interact with any of the three genes on the
GRN, but could not be affected by them. The morphogenetic field was defined by
an unidimensional array of 30 isogenic cells exposed to the morphogen
concentration gradient (Fig~\ref{fig:model}C). The initial concentration of
each gene product in all cells was set to 0.1 in all simulations.\\

@@

 \item {\bf Mutate GRNs randomly and evaluate fitness again.} Mutations
included changes in the  numerical values of degradation and diffusion
parameters and interaction strengths, and addition and removal of interactions
among genes and between the genes and the morphogen. If fitness of the mutated
GRN was greater or equal than that of the previous GRN, mutated GRN was saved
and the cycle continued from step 2. This cycle was repeated 50000 times, and a GRN
sampled at a given step and with a fitness score ≥ 0.95 was saved to a file as
long as its associated topology had not been sampled in previous steps.

>>>>

In our model the morphogen could interact with any of the three genes on the
GRN, but could not be affected by them. The morphogenetic field was defined
by an unidimensional array of 30 isogenic cells exposed to the morphogen
concentration gradient (Fig~\ref{fig:model}C). In multiple-input networks,
all the genes of a given cell are exposed to the same morphogen
concentration, given by an exponential decay function (see Morphogen
spatial distribution). The initial concentration of each gene product in
all cells was set to 0.1 in all simulations.\\

@@

 \item {\bf Mutate GRNs randomly and evaluate fitness again.} Three types
 of mutations were possible in our algorithm:
1) changes in the numerical value of the degradation parameter, 2) changes
in the numerical value of the diffusion parameter and 3) changes in the
numerical values of the interaction strengths. The type of mutation to be
performed was selected randomly with a probability of 0.15 for type 1 and
type 2 mutations and 0.7 for type 3 mutations. If type 3 mutation was
selected, either the interaction strength was set to zero (with a
probability of 0.2) or was changed randomly (with a probability of 0.8).
If fitness of the mutated GRN was greater or equal than that of the
previous GRN, mutated GRN was saved and the cycle continued from step 2.
This cycle was repeated 50000 times, and a GRN sampled at a given step
and with a fitness score ≥ 0.95 was saved to a file as
long as its associated topology had not been sampled in previous steps.
